\Large\bf FlexibleSUSY --- A spectrum generator generator for supersymmetric models

### 2014-06-06 doc/paper.tex
grammar: Note,  -->  Note

A general (non-constrained) softly broken SUSY model is defined by the
gauge group, the field content and mixings as well as the
superpotential and the soft-breaking Lagrangian.  In order to create a
spectrum generator for such a SUSY model with \fs, the aforementioned
model properties have to be defined in a SARAH model file.  The SARAH
model file can be put into the \code{sarah/<model>/} directory.  See
the SARAH manual \cite{Staub:2008uz,Staub:2013tta} for a detailed
explanation of how to write such a model file.  Note, that SARAH
already comes with a lot of predefined models, which can be used with
\fs immediately.

The model boundary conditions are defined in the \fs model file
\code{FlexibleSUSY.m}, which has to be located in the model directory
\code{models/<model>/}.  Note, that many example model files can
already be found in \code{model_files/}.  In the following it is
explained how the boundary conditions can be defined on the basis of
the CMSSM.  The application to other models is straightforward.  The
CMSSM model file reads:
%
\begin{lstlisting}[language=Mathematica]
FSModelName = "MSSM";

@@

  numerical value.  Note, that \fs GUT-normalizes all gauge couplings.

>>>>

A general (non-constrained) softly broken SUSY model is defined by the
gauge group, the field content and mixings as well as the
superpotential and the soft-breaking Lagrangian.  In order to create a
spectrum generator for such a SUSY model with \fs, the aforementioned
model properties have to be defined in a SARAH model file.  The SARAH
model file can be put into the \code{sarah/<model>/} directory.  See
the SARAH manual \cite{Staub:2008uz,Staub:2013tta} for a detailed
explanation of how to write such a model file.  Note that SARAH
already comes with a lot of predefined models, which can be used with
\fs immediately.

The model boundary conditions are defined in the \fs model file
\code{FlexibleSUSY.m}, which has to be located in the model directory
\code{models/<model>/}.  Note that many example model files can
already be found in \code{model_files/}.  In the following it is
explained how the boundary conditions can be defined on the basis of
the CMSSM.  The application to other models is straightforward.  The
CMSSM model file reads:
%
\begin{lstlisting}[language=Mathematica]
FSModelName = "MSSM";

@@

  numerical value.  Note that \fs GUT-normalizes all gauge couplings.
